\bf Landslide: \\ Systematic Dynamic Race Detection in Kernel-space

### 2012-04-25 design.tex
add inflight alg listing

Landslide's scheduling technique, called the {\em schedule in-flight}, involves successive triggering of timer interrupts to trigger context switches until the desired thread begins to run. % TODO: make an algorithm listing for the schedule-in-flight alg

>>>>

Landslide's scheduling technique, called the {\em schedule in-flight}, involves successive triggering of timer interrupts to trigger context switches until the desired thread begins to run. Algorithm~\ref{alg:inflight} shows how Landslide makes this happen.

One alternative, simpler method would be, when triggering a timer interrupt, to tell the guest kernel explicitly which thread should be run next. This would require the kernel programmer to write extra code in their timer handler and/or context switcher. We chose the ``in-flight'' approach instead, because it does not require additional kernel modifications.

\begin{algorithm*}[t!]
	\label{alg:inflight}
	\begin{algorithmic}
		\State {\em Global scheduler state.}
		\State bool schedule\_in\_flight;
		\State int target\_tid;
		\\
		\State {\em Per-thread state. (Updated elsewhere.)}
		\State bool in\_timer\_handler, in\_context\_switch;
		\State int current\_tid;
		\\
		\Function{scheduler\_update}{int eip}
			\If{schedule\_in\_flight}
				\State {\sc assert}(in\_timer\_handler || in\_context\_switch);
				\If { {\sc kernel\_exiting\_timer}(eip) || (!handling\_timer \&\& {\sc kernel\_exiting\_context\_switch}(eip))}
					\State {\em Then the kernel has just finished rescheduling and is about to resume normal thread execution.}
					\If {current\_tid != target\_tid}
						\State {\em The kernel switched to an undesirable thread. Keep the schedule operation ``in-flight''.}
						\State {\sc cause\_timer\_interrupt}();
					\Else
						\State {\em The in-flight schedule is ``landing''.}
						\State schedule\_in\_flight $\gets$ false;
					\EndIf
				\EndIf
			\ElsIf{{\sc need\_to\_preempt}()}
				\State target\_tid $\gets$ {\sc choose\_new\_thread}();
				\State schedule\_in\_flight $\gets$ true;
				\State {\sc cause\_timer\_interrupt}();
			\EndIf
		\EndFunction
	\end{algorithmic}
	\caption{The scheduling algorithm. This procedure for updating the scheduler's state is executed once per instruction, with a corresponding value for \texttt{eip} each time. The predicates on \texttt{eip} are part of the kernel instrumentation which tell what the guest kernel is doing at the current instruction.}
\end{algorithm*}
